Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 lower_bound.tex

We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that the regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.

>>>>

We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
\dkcomment{This was supposed to be a corollary (presumably in Section
  3) we would write that would show that
  in the special case $\TieDensity = 0$, the regret is constant.}
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that the regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.
